### 2012-04-11 trunk/tr-semanticsearchsurvey-data/intro.tex

\subsection{Outline}
The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}. Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches. Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}. Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}. After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}. Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, before we finally conclude in Section~\ref{sec:conclusion}.

>>>>

\subsection{Outline}
The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}. Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches. Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}. Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}. After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}, 
%Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, 
before we finally conclude in Section~\ref{sec:conclusion}.
